On the Synchronization Power of the OpenFlow Data Plane

### 2015-05-25 inband-sync.tex
made a fix in implementation section.

More precisely, the match part of a rule is 
a ternary pattern over packet \emph{header} fields.
The pattern is represented as a \emph{value} and a \emph{mask}. 
In the mask, certain header fields, e.g., port numbers or destination and source
addresses, can be \emph{wildcarded}, stipulating that their content does
not affect the match. 
Certain field, such as \emph{src}, \emph{dst}, \emph{metadata}, can be arbitrarily
bitmasked. 
In our implementations, we are going to use bitmasking of the metadata
field for performing conditional operations on  its content.   
For examples, \texttt{port=10.1.14.0, ff.ff.ff.f0} matches all packets
with source addresses in the range \texttt{10.1.14.0}--\texttt{10.1.14.127}.

@@

We now describe Algorithms~\ref{alg:claim}-\ref{alg:write} in more
detail. 
Each of the operations generates one or two FlowMod commands. 
The \textit{match} part in these commands specifies only the $64$bit meta-data
field in the header space, leaving the remaining fields in default
values.  
In defining the value and the mask of the math part, we 
use notation $a\concat b$ to represent a concatenation of two
$32$bit integers $a$ and $b$: $a\concat b := (a<<32)+b$.
We also write \texttt{1$\ldots$1} for  a $32$bit 
string of $1$'s used in a mask.  
%
The action part in these commands is defined as an integer, which in
practice can be implemented by a \emph{set meta-data} instruction where the written value is that integer.

@@

In order to check if an identifier is claimed, a controller tries to add the
a new entry setting the flag \texttt{\checko}, and using a different
action ($2$ instead of $1$), 
thereby inflicting a failure in case an entry with overlapping match value exists.
If the check succeeds, we delete the entry. 
In the example above above,
and their respective actions $a_1=x_1\concat c1$ and $a_2=x_2\concat c2$,  they overlap
with different actions iff $x_1=x_2$. Therefore, if one is used in \claimcheck after the other used in the claim operation,
a conflict is detected iff $x_1=x_2$, as desired.

>>>>

More precisely, the match part of a rule is 
a ternary pattern over packet \emph{header} fields.
The pattern is represented as a \emph{value} and a \emph{mask}. \liron{we need to discuss about this, I am not sure this description is accurate.}
In the mask, certain header fields, e.g., port numbers or destination and source
addresses, can be \emph{wildcarded}, stipulating that their content does
not affect the match. 
Certain field, such as \emph{src}, \emph{dst}, \emph{metadata}, can be arbitrarily
bitmasked. 
In our implementations, we are going to use bitmasking of the metadata
field for performing conditional operations on  its content.   
For examples, \texttt{port=10.1.14.0, ff.ff.ff.f0} matches all packets
with source addresses in the range \texttt{10.1.14.0}--\texttt{10.1.14.127}.

@@

We now describe Algorithms~\ref{alg:claim}-\ref{alg:compare} in more
detail. 
Each of the operations generates one or two FlowMod commands. 
The \textit{match} part in these commands specifies only the $64$bit meta-data
field in the header space, leaving the remaining fields in default
values.  
In defining the value and the mask of the math part, we 
use notation $a\concat b$ to represent a concatenation of two
$32$bit integers $a$ and $b$: $a\concat b := (a<<32)+b$.
We also write \texttt{1$\ldots$1} for  a $32$bit 
string of $1$'s used in a mask.  
%
The action part in these commands is defined as an integer, which in
practice can be implemented by a \emph{set meta-data} instruction where the written value is that integer.

@@

In order to check if an identifier is claimed, a controller tries to add the
a new entry setting the flag \texttt{\checko}, and using a different
action ($2$ instead of $1$), 
thereby inflicting a failure in case an entry with overlapping match value exists.
If the check succeeds, we delete the entry. 
Con sidering, $m_1$ and $m_2$ from the example above,
with respective actions $a_1=1$ and $a_2=2$,  they overlap
with different actions iff $x_1=x_2$. Therefore, if $m_1$ is used in \claimcheck after $m_2$ used in the claim operation,
a conflict is detected iff $x_1=x_2$, as desired.
